---
title: "DaparToolshed data using Bioconductor's ExperimentHub"
author:
-name: Samuel Wieczorek
package: DaparToolshedData
date: "`r doc_date()`"
vignette: >
  %\VignetteIndexEntry{DaparToolshd data using Bioconductor's ExperimentHub}
  %\VignetteEngine{knitr::rmarkdown}
  %%\VignetteKeywords{Mass Spectrometry, MS, MSMS, Proteomics, Metabolomics}
  %\VignetteEncoding{UTF-8}
output: 
  BiocStyle::html_document:
    toc_float: true
---


Mass-spectrometry based UPS proteomics data sets from Ramus C, 
Hovasse A, Marcellin M, Hesse AM, Mouton-Barbosa E, Bouyssie D, 
Vaca S, Carapito C, Chaoui K, Bruley C, Garin J, Cianferani S, 
Ferro M, Dorssaeler AV, Burlet-Schiltz O, Schaeffer C, Coute Y, 
Gonzalez de Peredo A. 
Spiked proteomic standard dataset for testing label-free 
quantitative software and statistical methods. Data Brief. 2015 
Dec 17;6:286-94 and Giai Gianetto, Q., Combes, F., Ramus, C., 
Bruley, C., Coute, Y., Burger, T. (2016). Calibration plot for 
proteomics: A graphical tool to visually check the assumptions 
underlying FDR control in quantitative experiments. Proteomics, 
16(1), 29-32.


```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
```

# Introduction

The `DaparToolshedData` package provides example quantitative data from 
proteomics experiments. The data are served through the
`ExperimentHub` infrastructure, which allows download them only ones
and cache them for further use. Currently available data are summarised
in the table below and details in the next section.

```{r data}
library("DaparToolshedData")
DT::datatable(DaparToolshedData())
```

# Installation

To install the package:

```{r install1, eval = FALSE}
if (!require("BiocManager"))
    install.packages("BiocManager")

BiocManager::install("DaparToolshedData")
```


# Available data

Load datasets with (example for the Exp1_R25_prot dataset)

```{r, eval = TRUE}
GetData('Exp1_R25_prot')
```


# sessionInfo()

```{r sessionInfo}
sessionInfo()
```